Many Analystis Project

### 2022-02-06 analysis.Rmd
Update analysis.Rmd

dp2<-ggdag::ggdag_adjustment_set(dg2, node_size = 14, text = FALSE, use_labels = "label") +
  theme(legend.position = "bottom") +
  theme_dag() + ggtitle("Adjustment set for Religious Service
assuming service does not change from distress")

dp2

@@

dg1

@@

dl2<-ggdag::ggdag_adjustment_set(dpL, node_size = 14, text = FALSE, use_labels = "label") +
  theme(legend.position = "bottom") +
  theme_dag() + ggtitle("Adjustment set for Anxiety causing Belief in God")
dl2

>>>>

dg0<-ggdag::ggdag_adjustment_set(dg2, node_size = 14, text = FALSE, use_labels = "label") +
  theme(legend.position = "bottom") +
  theme_dag() + ggtitle("Adjustment set for religious service
assuming service does not change from distress")

dp0

@@

dg1
```

Save image

```{r dg1, eval=FALSE}
# save graph
ggsave(
  dg1,
  path = here::here("Figs"),
  width = 10,
  height = 5,
  units = "in",
  filename = "dag_belief.jpg",
  device = 'jpeg',
  limitsize = FALSE,
  dpi = 1200
)

```{r dp0, eval=FALSE}
# save graph
ggsave(
  dg1,
  path = here::here("Figs"),
  width = 10,
  height = 5,
  units = "in",
  filename = "dag_church.jpg",
  device = 'jpeg',
  limitsize = FALSE,
  dpi = 1200
)

@@

dl2<-ggdag::ggdag_adjustment_set(dpL, node_size = 14, text = FALSE, use_labels = "label") +
  theme(legend.position = "bottom") +
  theme_dag() + ggtitle("Adjustment set assuming anxiety causes belief in God")
dl2
